---
title: Developing Data Products course - Assignment Week 4 - Shiny Application and
  Reproducible Pitch
author: "Rudradip Misra"
date: "January 29, 2019"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

 - This presentation is one half of the assignemnt of week 4, ***Developing Data Products course from Coursera*** (<https://www.coursera.org/learn/data-products>). 
 
 -It is meant to describe and pitch information about an app developed through Shiny to help property investors determine profitability of a specific property they are interested in investing in. 

 

## Application

 - The second half of the mentioned assignment was to develop a web application. The application was named ***Investment Property***. 
 

 - This application shows an example of making a web application using R and [Shiny](https://shiny.rstudio.com) framework together.
 
## Description
 
 - It is meant to describe and pitch information about an app developed through Shiny to help property investors determine profitability of a specific property they are interested in investing in.
 
 In the application, anyone who is interested in purchasing property for investment purposes can input the purchase price or market value of a property and derive a range of weekly rents necessary to make a profit on the property. The output is generated through calculations programmed in R.
 
 - The application and the current presentation source codes can be found at <https://github.com/rudradip/Week4DDP> and <https://rudradip-misra.shinyapps.io/Week4DDP/>. The application comprises 2 files: *ui.R* (UI), *server.R* (backend) . 
 
## Example R Code


An example of how the R code calculates the weekly profit or deficit for the property investor is below. Assuming the property costs the investor $200 per week and the weekly rent is $350. After deducting the quarterly water fees of $50 and the weekly community fees of $10, the property inverstor will earn a $136 weekly profit.

: 
```{r  echo = TRUE}

rent<-350
water<-50
fees<-10
mortgage<-200
  result <- (rent * 52 - (water) * 4 - fees * 52 - mortgage * 52) / 52
  return(round(result, digits = 2))

```

## Conclusion


This app can be a very useful tool for property investors looking to do a quick calculation to deterine profitability. The github repository containing the Shiny programs (ui.R and server.R) are found here:

https://github.com/rudradip/Week4DDP
